Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-23 talk/iwtc11/paper.tex
compactifying
use a single standard deviation per binary
explain the shorter names

XXX we either need to explain that we use C++ or consistently use C
\begin{figure*}
\begin{center}
{\smaller
\begin{tabular}{|l|r|r|r|r|r|r|}
\hline
 & CPython & Psyco & PyPy no LP & PyPy & GCC -O2 & GCC -O3\\
\hline
conv3(array(1e5)) & 77.89 & 9.52 & 1.77 $\pm$ 0.06 & 0.68 $\pm$ 0.02 & 0.70 $\pm$ 0.05 & 0.59 $\pm$ 0.01\\
\hline
conv3(array(1e6)) & 77.15 & 9.58 & 1.69 $\pm$ 0.01 & 0.77 $\pm$ 0.01 & 0.84 $\pm$ 0.05 & 0.74 $\pm$ 0.01\\
\hline
conv3x3(Array2D(1000x1000)) & 23.72 & 12.77 & 0.07 $\pm$ 0.00 & 0.05 $\pm$ 0.03 & 0.24 $\pm$ 0.00 & 0.25 $\pm$ 0.01\\
\hline
conv3x3(Array2D(1000000x3)) & 23.85 & 12.77 & 0.10 $\pm$ 0.00 & 0.07 $\pm$ 0.00 & 0.27 $\pm$ 0.01 & 0.27 $\pm$ 0.01\\
\hline
conv5(array(1e5)) & 122.54 & 16.67 & 1.86 $\pm$ 0.02 & 1.05 $\pm$ 0.03 & 1.03 $\pm$ 0.05 & 0.65 $\pm$ 0.01\\
\hline
conv5(array(1e6)) & 125.77 & 16.80 & 1.92 $\pm$ 0.03 & 1.09 $\pm$ 0.02 & 1.07 $\pm$ 0.05 & 0.80 $\pm$ 0.01\\
\hline
dilate3x3(Array2D(1000x1000)) & 23.29 & 12.99 & 0.41 $\pm$ 0.04 & 0.39 $\pm$ 0.01 & 0.26 $\pm$ 0.00 & 0.26 $\pm$ 0.01\\
\hline
sobel(Array2D(1000x1000)) & - & - & - & - & 0.19 $\pm$ 0.01 & 0.20 $\pm$ 0.01\\
\hline
%sobel\_uint8(NoBorderPadded) & 476.72 & 275.50 & 1.05 $\pm$ 0.01 & 0.51 $\pm$ 0.00 & - & -\\
%\hline
sqrt(Fix16) & 744.35 & 421.65 & 3.93 $\pm$ 0.11 & 2.14 $\pm$ 0.02 & 0.97 $\pm$ 0.02 & 0.96 $\pm$ 0.01\\
\hline
sqrt(float) & 24.21 & 5.52 & 1.36 $\pm$ 0.03 & 1.00 $\pm$ 0.00 & 0.98 $\pm$ 0.00 & 0.98 $\pm$ 0.00\\
\hline
sqrt(int) & 20.84 & 1.78 & 2.26 $\pm$ 0.01 & 1.82 $\pm$ 0.01 & 0.81 $\pm$ 0.01 & 0.80 $\pm$ 0.01\\
\hline

\end{tabular}
}
\end{center}
\label{fig:benchmarks}
\caption{Benchmark Results in Seconds}
\end{figure*}

>>>>

XXX we either need to explain that we use C++ or consistently use C
\begin{figure}
\begin{center}
{\smaller
\begin{tabular}{|l|r|r|r|r|r|r|}
\hline
 & CPython & Psyco & PyPy  & PyPy & GCC \\
 &         &       & no LP &      & -O3 \\
\hline
conv3(1e5) & 77.89 & 9.52 & 1.77  & 0.68 &  0.59 \\
\hline
conv3(1e6) & 77.15 & 9.58 & 1.69  & 0.77 &  0.74 \\
\hline
conv3x3(1000) & 23.72 & 12.77 & 0.07  & 0.05 &  0.25 \\
\hline
conv3x3(3) & 23.85 & 12.77 & 0.10  & 0.07  &  0.27 \\
\hline
conv5(1e5) & 122.54 & 16.67 & 1.86  & 1.05 &  0.65\\
\hline
conv5(1e6) & 125.77 & 16.80 & 1.92 & 1.09 &  0.80 \\
\hline
dilate3x3(1000) & 23.29 & 12.99 & 0.41  & 0.39 &  0.26 \\
\hline
sobel(1000) & - & - & - & - & 0.20 \\
\hline
sqrt(Fix16) & 744.35 & 421.65 & 3.93  & 2.14  & 0.96 \\
\hline
sqrt(float) & 24.21 & 5.52 & 1.36 & 1.00 & 0.98\\
\hline
sqrt(int) & 20.84 & 1.78 & 2.26 & 1.82  & 0.80 \\
\hline
\hline
Variations & - & - & $\pm 0.03$ & $\pm 0.01$ & $\pm 0.01$ \\
\hline
\end{tabular}
}
\end{center}
\label{fig:benchmarks}
\caption{Benchmark Results in Seconds. Arrays of length $10^5$ and
  $10^6$ and matrixes of size $1000\times 1000$ and $1000000 \times
  3$ are used. This is indicated in the leftmost column. For the
  matrixes, only the number of rows are listed.} 
\end{figure}
